Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
typos

Conditional termination is illustrated by the program in Figure~\ref{fig:motivation.h},
which is encoded as:
\begin{align*}
            I(\langle x, y \rangle) & \triangleq y = 1 \\
            G(\langle x, y \rangle) & \triangleq x > 0 \\
            T(\langle x, y \rangle, \langle x', y' \rangle) & \triangleq x' = x - y \wedge y' = y 
\end{align*}
If the initial states $I$ are ignored this loop cannot be shown to terminate, since any state with $y = 0$ and $x > 0$
would lead to a non-terminating execution.

@@

We use Counterexample Guided Inductive Synthesis
(CEGIS)~\cite{lezama-thesis,sketch, DBLP:conf/iclp/BrainCVF06} to find an
$\mathcal{L}$-program satisfying our specification.  The core of the CEGIS
algorithm is the refinement loop shown in Fig.~\ref{fig:abstract-refinement}
and detailed in Algorithm~\ref{alg:cegis}.

>>>>

Conditional termination is illustrated by the program in Figure~\ref{fig:motivation.h},
which is encoded as:
\begin{align*}
            I(\langle x, y \rangle) & \triangleq y = 1 \\
            G(\langle x, y \rangle) & \triangleq x > 0 \\
            T(\langle x, y \rangle, \langle x', y' \rangle) & \triangleq x' = x - y \wedge y' = y 
\end{align*}
If the initial states $I$ are ignored, this loop cannot be shown to terminate, since any state with $y = 0$ and $x > 0$
would lead to a non-terminating execution.

@@

We use Counterexample Guided Inductive Synthesis
(CEGIS)~\cite{lezama-thesis,sketch, DBLP:conf/iclp/BrainCVF06} to find an
$\mathcal{L}$-program satisfying our specification.  The core of the CEGIS
algorithm is the refinement loop shown in Figure~\ref{fig:abstract-refinement}
and detailed in Algorithm~\ref{alg:cegis}.
